Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training with GPUs

### 2020-12-24 NEUROC/sec2-review-of-graph-neural-network.tex
修正了sec2的一些拼写错误

In the inpug layer, A GNN receives a graph $\mathcal{G}$ as the input.
%
Every vertex $v_x$ in $\mathcal{G}$ is attached with a feature vector $\boldsymbol{v}_x$ to describe the properties of the vertex.
%
Every edge $e_{y,x}$ of $\mathcal{G}$ may also be attached with a feature vector $\boldsymbol{e}_{y,x}$.
%
The input layer of a GNN receives feature vectors from all vertices and passes the feature vectors to the first GNN layer (i.e. GNN layer 0).

@@

Based on the multi-head mechanism, GaAN \cite{zhang2018_gaan} introduces a convolutional subnetwork to control the weight of each head.
%
Each GaAN layer consists of four sub-layers (as defined in Table~\ref{tab:gnn_overview_edge} and Table~\ref{tab:gnn_overview_vertex}).
%
The first two sub-layers are similar to GAT, and the last two sub-layers build the convolutional subnetwork.
%
The first sub-layer aims to get the sum of attention weights of every vertex in all heads $\MyVec{h}^{l,0}_x$.
The second sub-layer aggregates the hidden vectors from the previous GaAN layer with the normalized attention weights for all heads $\alpha_{(k)}$.
The third and fourth sub-layers aggregate the hidden vectors from the GaAN previous layer with the element-wise max and mean operators separately.
The vertex updating funciton $\gamma^{l,4}$ of the fourth sub-layer uses the hidden vectors of the last two sub-layers $\MyVec{h}^{l, 1}_x, \MyVec{h}^{l, 2}_x$ to generate the output hidden vector $\MyVec{h}^{l+1}_x$.

@@

By default, GNNs are trained in a full-batch way, using the whole graph in each iteration.
%
The full-batch gradient descent has two disadvantages \cite{chiang2019_cluster_gcn}:
%
(1) it has to cache intermediate results of all vertices in the forward phase, which consumes lots of memory space;
%
(2) it updates the model parameters only once for each epoch, slowing the convergence of gradient descent.

@@

In the implementation in PyG, the model parameters of GNNs resid on the GPU side and the input graph resides on the host side.
%
To process an epoch, PyG samples the original graph in the main memory and generates several batches for the epoch.
%
For each batch, PyG sends the sampled subgraph to the GPU, propagates the feature vectors of the sampled subgraph from the input layer to the prediction layer, calculates the gradients on the subgraph, and updates the model parameters based on the gradients directly on the GPU.
%
With the sampling techniques, the model parameters are updated by a stochastic gradient descent optimizer.
%
PyG conducts the evaluation phase every several epochs or batches (either on the CPU side or the GPU side) to determine whether to stop the training.

>>>>

In the input layer, A GNN receives a graph $\mathcal{G}$ as the input.
%
Every vertex $v_x$ in $\mathcal{G}$ is attached with a feature vector $\boldsymbol{v}_x$ to describe the properties of the vertex.
%
Every edge $e_{y,x}$ of $\mathcal{G}$ may also be attached with a feature vector $\boldsymbol{e}_{y,x}$.
%
The input layer of a GNN receives feature vectors from all vertices and passes the feature vectors to the first GNN layer (i.e. GNN layer 0).

@@

Based on the multi-head mechanism, GaAN \cite{zhang2018_gaan} introduces a convolutional subnetwork to control the weight of each head.
%
Each GaAN layer consists of four sub-layers (as defined in Table~\ref{tab:gnn_overview_edge} and Table~\ref{tab:gnn_overview_vertex}).
%
The first two sub-layers are similar to GAT, and the last two sub-layers build the convolutional subnetwork.
%
The first sub-layer aims to get the sum of attention weights of every vertex in all heads $\MyVec{h}^{l,0}_x$.
The second sub-layer aggregates the hidden vectors from the previous GaAN layer with the normalized attention weights for all heads $\alpha_{(k)}$.
The third and fourth sub-layers aggregate the hidden vectors from the GaAN previous layer with the element-wise max and mean operators separately.
The vertex updating funciton $\gamma^{l,3}$ of the fourth sub-layer uses the hidden vectors of the last two sub-layers $\MyVec{h}^{l, 1}_x, \MyVec{h}^{l, 2}_x$ to generate the output hidden vector $\MyVec{h}^{l+1}_x$.

@@

By default, GNNs are trained in a full-batch way, using the whole graph in each iteration.
%
But the full-batch gradient descent has two disadvantages \cite{chiang2019_cluster_gcn}:
%
(1) it has to cache intermediate results of all vertices in the forward phase, consuming lots of memory space, which is not scalable;
%
(2) it updates the model parameters only once for each epoch, slowing the convergence of gradient descent.

@@

In the implementation in PyG, the model parameters of GNNs reside on the GPU side and the input graph resides on the host side.
%
To process an epoch, PyG samples the original graph in the main memory and generates several batches for the epoch.
%
For each batch, PyG sends the sampled subgraph to the GPU, propagates the feature vectors of the sampled subgraph from the input layer to the prediction layer, calculates the gradients on the subgraph, and updates the model parameters based on the gradients directly on the GPU.
%
With the sampling techniques, the model parameters are updated by a stochastic gradient descent optimizer.
%
PyG conducts the evaluation phase every several epochs or batches (either on the CPU side or the GPU side) to determine whether to stop the training.
